---
title: "Main Text Analyses"
author: "Reg"
date: "4/14/2022"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)

# data prep 
source("BLM-elevation_data-prep.R")

# palettes that work for our color-blind friends
source("BLM-elevation_palettes.R")

# useful plot function(s)
source("BLM-elevation_useful-plots.R")

# reporting packages
library(htmlTable)
library(interactions)
library(psych)
library(report)
library(tidyverse)
library(sjPlot)
library(kableExtra)
library(knitr)
library(yarrr)
library(emmeans)
library(dplyr)
library(Hmisc)
library(mediation)

```


### Correlation between conservatism and police funding

```{r}
pear_1 <- cor.test(formula = ~ police_funding + conservativism_overall, data = pilot$df, method = "pearson", exact = F)
pear_2 <- cor.test(formula = ~ police_funding + conservativism_overall, data = study1$df, method = "pearson", exact = F)
pear_3 <- cor.test(formula = ~ police_funding + conservativism_overall, data = study2$df, method = "pearson", exact = F)

list_of_study <-
  list(
    "pilot",
    "study 1",
    "study 2"
  )

list_of_pearson <-
  list(
    pear_1$estimate,
    pear_2$estimate,
    pear_3$estimate
  )

list_of_pearson_p <-
  list(
    pear_1$p.value,
    pear_2$p.value,
    pear_3$p.value
  )

pearson_parameters <- tibble(
  study = list_of_study,
  correlation_coefficient = list_of_pearson,
  p_value = list_of_pearson_p
)

pearson_parameters %>%
  kable(caption = "pearson correlation: conservatism and police funding") %>%
  kable_styling()


```

### Correlation between conservatism and police idealism

```{r}
pear_1 <- cor.test(formula = ~ idealism_police + conservativism_overall, data = pilot$df, method = "pearson", exact = F)
pear_2 <- cor.test(formula = ~ idealism_police + conservativism_overall, data = study1$df, method = "pearson", exact = F)
pear_3 <- cor.test(formula = ~ idealism_police + conservativism_overall, data = study2$df, method = "pearson", exact = F)

list_of_study <-
  list(
    "pilot",
    "study 1",
    "study 2"
  )

list_of_pearson <-
  list(
    pear_1$estimate,
    pear_2$estimate,
    pear_3$estimate
  )

list_of_pearson_p <-
  list(
    pear_1$p.value,
    pear_2$p.value,
    pear_3$p.value
  )

pearson_parameters <- tibble(
  study = list_of_study,
  correlation_coefficient = list_of_pearson,
  p_value = list_of_pearson_p
)

pearson_parameters %>%
  kable(caption = "pearson correlation: conservatism and police idealism") %>%
  kable_styling()
```

### Correlation between conservatism and BLM idealism

```{r}

pear_1 <- cor.test(formula = ~ idealism_blm + conservativism_overall, data = study2$df, method = "pearson", exact = F)


list_of_study <-
  list(
    "study 2"
  )

list_of_pearson <-
  list(
    pear_1$estimate
  )

list_of_pearson_p <-
  list(
    pear_1$p.value
  )

pearson_parameters <- tibble(
  study = list_of_study,
  correlation_coefficient = list_of_pearson,
  p_value = list_of_pearson_p
)

pearson_parameters %>%
  kable(caption = "pearson correlation: conservatism and BLM idealism") %>%
  kable_styling()
```

### Interaction between political orientation and video condition on elevation

```{r}
fit_1 <- lm(elevation ~ conservativism_overall * condition, data = study1$df)
fit_2 <- lm(elevation ~ conservativism_overall * condition, data = study2$df)

interaction_1 <- probe_interaction(fit_1,
           pred = conservativism_overall,
           modx = condition,
           digits = 3)


interaction_2 <- probe_interaction(fit_2,
           pred = conservativism_overall,
           modx = condition,
           digits = 3)


format(interaction_1$simslopes$slopes, digits = 3) %>%
  kbl(caption = "simple slopes for study 1") %>%
  kable_styling()

interaction_contrasts_1 <- emtrends(fit_1, pairwise ~ condition, var = "conservativism_overall", )

kbl(interaction_contrasts_1$contrasts, digits = c(2, 2, 2, 2, 2, 20), caption = "estimate for interaction term in study 1") %>%
  kable_styling()

format(interaction_2$simslopes$slopes, digits = 3) %>%
  kbl(caption = "simple slopes for study 2") %>%
  kable_styling()

interaction_contrasts_2 <- emtrends(fit_2, pairwise ~ condition, var = "conservativism_overall", )

kbl(interaction_contrasts_2$contrasts, digits = c(2, 2, 2, 2, 2, 20), caption = "estimate for interaction terms in study 2") %>%
  kable_styling()

```
### Interaction between political orientation and video condition on funding preferences



```{r}
fit_1 <- lm(police_funding ~ conservativism_overall * condition, data = study1$df)
fit_2 <- lm(police_funding ~ conservativism_overall * condition, data = study2$df)

interaction_1 <- probe_interaction(fit_1,
           pred = conservativism_overall,
           modx = condition,
           digits = 3)


interaction_2 <- probe_interaction(fit_2,
           pred = conservativism_overall,
           modx = condition,
           digits = 3)


format(interaction_1$simslopes$slopes, digits = 3) %>%
  kbl(caption = "simple slopes for study 1") %>%
  kable_styling()

interaction_contrasts_1 <- emtrends(fit_1, pairwise ~ condition, var = "conservativism_overall", )

kbl(interaction_contrasts_1$contrasts, digits = c(2, 2, 2, 2, 2, 20), caption = "estimate for interaction term in study 1") %>%
  kable_styling()

format(interaction_2$simslopes$slopes, digits = 3) %>%
  kbl(caption = "simple slopes for study 2") %>%
  kable_styling()

interaction_contrasts_2 <- emtrends(fit_2, pairwise ~ condition, var = "conservativism_overall", )

kbl(interaction_contrasts_2$contrasts, digits = c(2, 2, 2, 2, 2, 20), caption = "estimate for interaction terms in study 2") %>%
  kable_styling()

```



### Interaction between elevation and video condition on funding preferences



```{r}
fit_1 <- lm(police_funding ~ elevation * condition, data = study1$df)
fit_2 <- lm(police_funding ~ elevation * condition, data = study2$df)

interaction_1 <- probe_interaction(fit_1,
           pred = elevation,
           modx = condition,
           digits = 3)


interaction_2 <- probe_interaction(fit_2,
           pred = elevation,
           modx = condition,
           digits = 3)


format(interaction_1$simslopes$slopes, digits = 3) %>%
  kbl(caption = "simple slopes for study 1") %>%
  kable_styling()

interaction_contrasts_1 <- emtrends(fit_1, pairwise ~ condition, var = "elevation", )

kbl(interaction_contrasts_1$contrasts, digits = c(3, 3, 3, 3, 3, 20), caption = "estimate for interaction term in study 1") %>%
  kable_styling()

format(interaction_2$simslopes$slopes, digits = 3) %>%
  kbl(caption = "simple slopes for study 2") %>%
  kable_styling()

interaction_contrasts_2 <- emtrends(fit_2, pairwise ~ condition, var = "elevation", )

kbl(interaction_contrasts_2$contrasts, digits = c(3, 3, 3, 3, 3, 20), caption = "estimate for interaction terms in study 2") %>%
  kable_styling()

```




### Spearman and Pearson correlations betweeen conservatism and elevation by condition

```{r}
rho_1 <- cor.test(formula = ~ elevation + conservativism_overall, data = pilot$df %>% filter(condition == "BLM"), method = "spearman", exact = F)
rho_2 <- cor.test(formula = ~ elevation + conservativism_overall, data = study1$df %>% filter(condition == "control"), method = "spearman", exact = F)
rho_3 <- cor.test(formula = ~ elevation + conservativism_overall, data = study1$df %>% filter(condition == "BLM"), method = "spearman", exact = F)
rho_4 <- cor.test(formula = ~ elevation + conservativism_overall, data = study2$df %>% filter(condition == "control"), method = "spearman", exact = F)
rho_5 <- cor.test(formula = ~ elevation + conservativism_overall, data = study2$df %>% filter(condition == "BLM"), method = "spearman", exact = F)
rho_6 <- cor.test(formula = ~ elevation + conservativism_overall, data = study2$df %>% filter(condition == "BtB"), method = "spearman", exact = F)
pear_1 <- cor.test(formula = ~ elevation + conservativism_overall, data = pilot$df %>% filter(condition == "BLM"), method = "pearson", exact = F)
pear_2 <- cor.test(formula = ~ elevation + conservativism_overall, data = study1$df %>% filter(condition == "control"), method = "pearson", exact = F)
pear_3 <- cor.test(formula = ~ elevation + conservativism_overall, data = study1$df %>% filter(condition == "BLM"), method = "pearson", exact = F)
pear_4 <- cor.test(formula = ~ elevation + conservativism_overall, data = study2$df %>% filter(condition == "control"), method = "pearson", exact = F)
pear_5 <- cor.test(formula = ~ elevation + conservativism_overall, data = study2$df %>% filter(condition == "BLM"), method = "pearson", exact = F)
pear_6 <- cor.test(formula = ~ elevation + conservativism_overall, data = study2$df %>% filter(condition == "BtB"), method = "pearson", exact = F)


list_of_study <-
  list(
    "pilot",
    "study 1",
    "study 1",
    "study 2",
    "study 2",
    "study 2"
  )


list_of_condition <-
  list(
    "BLM",
    "control",
    "BLM",
    "control",
    "BLM",
    "BtB"
  )

list_of_rho <-
  list(
    rho_1$estimate,
    rho_2$estimate,
    rho_3$estimate,
    rho_4$estimate,
    rho_5$estimate,
    rho_6$estimate
  )

list_of_rho_p <-
  list(
    rho_1$p.value,
    rho_2$p.value,
    rho_3$p.value,
    rho_4$p.value,
    rho_5$p.value,
    rho_6$p.value
  )

rho_parameters <- tibble(
  study = list_of_study,
  condition = list_of_condition,
  rho = list_of_rho,
  p_value = list_of_rho_p
)

rho_parameters %>%
  kable(caption = "spearman correlations between conservatism and elevation") %>%
  kable_styling()

list_of_pearson <-
  list(
    pear_1$estimate,
    pear_2$estimate,
    pear_3$estimate,
    pear_4$estimate,
    pear_5$estimate,
    pear_6$estimate
  )

list_of_pearson_p <-
  list(
    pear_1$p.value,
    pear_2$p.value,
    pear_3$p.value,
    pear_4$p.value,
    pear_5$p.value,
    pear_6$p.value
  )

pearson_parameters <- tibble(
  study = list_of_study,
  condition = list_of_condition,
  correlation_coefficient = list_of_pearson,
  p_value = list_of_pearson_p
)

pearson_parameters %>%
  kable(caption = "pearson correlations between conservatism and elevation") %>%
  kable_styling()

```

### Spearman and Pearson correlations betweeen funding and elevation by condition

```{r}
rho_1 <- cor.test(formula = ~ elevation + police_funding, data = pilot$df %>% filter(condition == "BLM"), method = "spearman", exact = F)
rho_2 <- cor.test(formula = ~ elevation + police_funding, data = study1$df %>% filter(condition == "control"), method = "spearman", exact = F)
rho_3 <- cor.test(formula = ~ elevation + police_funding, data = study1$df %>% filter(condition == "BLM"), method = "spearman", exact = F)
rho_4 <- cor.test(formula = ~ elevation + police_funding, data = study2$df %>% filter(condition == "control"), method = "spearman", exact = F)
rho_5 <- cor.test(formula = ~ elevation + police_funding, data = study2$df %>% filter(condition == "BLM"), method = "spearman", exact = F)
rho_6 <- cor.test(formula = ~ elevation + police_funding, data = study2$df %>% filter(condition == "BtB"), method = "spearman", exact = F)
pear_1 <- cor.test(formula = ~ elevation + police_funding, data = pilot$df %>% filter(condition == "BLM"), method = "pearson", exact = F)
pear_2 <- cor.test(formula = ~ elevation + police_funding, data = study1$df %>% filter(condition == "control"), method = "pearson", exact = F)
pear_3 <- cor.test(formula = ~ elevation + police_funding, data = study1$df %>% filter(condition == "BLM"), method = "pearson", exact = F)
pear_4 <- cor.test(formula = ~ elevation + police_funding, data = study2$df %>% filter(condition == "control"), method = "pearson", exact = F)
pear_5 <- cor.test(formula = ~ elevation + police_funding, data = study2$df %>% filter(condition == "BLM"), method = "pearson", exact = F)
pear_6 <- cor.test(formula = ~ elevation + police_funding, data = study2$df %>% filter(condition == "BtB"), method = "pearson", exact = F)


list_of_study <-
  list(
    "pilot",
    "study 1",
    "study 1",
    "study 2",
    "study 2",
    "study 2"
  )


list_of_condition <-
  list(
    "BLM",
    "control",
    "BLM",
    "control",
    "BLM",
    "BtB"
  )

list_of_rho <-
  list(
    rho_1$estimate,
    rho_2$estimate,
    rho_3$estimate,
    rho_4$estimate,
    rho_5$estimate,
    rho_6$estimate
  )

list_of_rho_p <-
  list(
    rho_1$p.value,
    rho_2$p.value,
    rho_3$p.value,
    rho_4$p.value,
    rho_5$p.value,
    rho_6$p.value
  )

rho_parameters <- tibble(
  study = list_of_study,
  condition = list_of_condition,
  rho = list_of_rho,
  p_value = list_of_rho_p
)

rho_parameters %>%
  kable(caption = "spearman correlations between funding and elevation") %>%
  kable_styling()

list_of_pearson <-
  list(
    pear_1$estimate,
    pear_2$estimate,
    pear_3$estimate,
    pear_4$estimate,
    pear_5$estimate,
    pear_6$estimate
  )

list_of_pearson_p <-
  list(
    pear_1$p.value,
    pear_2$p.value,
    pear_3$p.value,
    pear_4$p.value,
    pear_5$p.value,
    pear_6$p.value
  )

pearson_parameters <- tibble(
  study = list_of_study,
  condition = list_of_condition,
  correlation_coefficient = list_of_pearson,
  p_value = list_of_pearson_p
)

pearson_parameters %>%
  kable(caption = "pearson correlations between funding and elevation") %>%
  kable_styling()

```


### main effect of condition on elevation

Note that for the study 2 pairwise comparisons, p values are less than 2.62e-14--the package can't produce values any lower.

```{r}

pirateplot(formula = elevation ~ condition,
           data = study1$df,
           main = "elevation by condition study 1",
           theme = 3,
           xlab = "condition",
           ylab = "elevation",
           cex.names = .75,
           cex.lab = .75,
           pal = "espresso")

aov_1 <- aov(elevation ~ condition, data = study1$df)
summary(aov_1)
tukey_aov_1 <- TukeyHSD(aov_1)
tukey_aov_1

study1$df %>% 
  group_by(condition) %>%
  summarise(
    mean = mean(elevation, na.rm = T),
    sd = sd(elevation, na.rm = T)
    ) %>%
  kable(caption = "descriptive stats study 1") %>%
  kable_styling()



pirateplot(formula = elevation ~ condition,
           data = study2$df,
           main = "elevation by condition study 2",
           theme = 3,
           xlab = "condition",
           ylab = "elevation",
           cex.names = .75,
           cex.lab = .75,
           pal = "espresso")

aov_2 <- aov(elevation ~ condition, data = study2$df)
summary(aov_2)
tukey_aov_2 <- TukeyHSD(aov_2)
tukey_aov_2

study2$df %>% 
  group_by(condition) %>%
  summarise(
    mean = mean(elevation, na.rm = T),
    sd = sd(elevation, na.rm = T)
    ) %>%
  kable(caption = "descriptive stats study 2") %>%
  kable_styling()
```



### main effect of condition on funding

```{r}

pirateplot(formula = police_funding ~ condition,
           data = study1$df,
           main = "police funding by condition study 1",
           theme = 3,
           xlab = "condition",
           ylab = "police funding",
           cex.names = .75,
           cex.lab = .75,
           pal = "espresso")

aov_1 <- aov(police_funding ~ condition, data = study1$df)
summary(aov_1)
tukey_aov_1 <- TukeyHSD(aov_1)
tukey_aov_1

study1$df <- study1$df %>%
  mutate(elevation = as.numeric(elevation)) %>%
  mutate(police_funding = as.numeric(police_funding)) %>%
  mutate(condition = factor(condition, ordered = F))

study1$df$condition <- relevel(study1$df$condition, ref = "control")

med_1 <- lm(police_funding ~ condition, data = study1$df)
med_2 <- lm(elevation ~ condition, data = study1$df)
med_3 <- lm(police_funding ~ elevation + condition, data = study1$df)
med_results <- mediation::mediate(med_2, med_3, treat = "condition", mediator = "elevation")
summary(med_results)

study1$df %>% 
  group_by(condition) %>%
  summarise(
    mean = mean(police_funding, na.rm = T),
    sd = sd(police_funding, na.rm = T)
    ) %>%
  kable(caption = "descriptive stats study 1") %>%
  kable_styling()

study2$df <- study2$df %>%
  mutate(elevation = as.numeric(elevation)) %>%
  mutate(police_funding = as.numeric(police_funding)) %>%
  mutate(condition = factor(condition, ordered = F))

study2$df$condition <- relevel(study2$df$condition, ref = "control")

med_1 <- lm(police_funding ~ condition, data = study2$df %>% filter(condition != "BtB"))
med_2 <- lm(elevation ~ condition, data = study2$df %>% filter(condition != "BtB"))
med_3 <- lm(police_funding ~ elevation + condition, data = study2$df %>% filter(condition != "BtB"))
med_results <- mediation::mediate(med_2, med_3, treat = "condition", mediator = "elevation")
summary(med_results)


pirateplot(formula = police_funding ~ condition,
           data = study2$df,
           main = "police funding by condition study 2",
           theme = 3,
           xlab = "condition",
           ylab = "police funding",
           cex.names = .75,
           cex.lab = .75,
           pal = "espresso")

aov_2 <- aov(police_funding ~ condition, data = study2$df)
summary(aov_2)
tukey_aov_2 <- TukeyHSD(aov_2)
tukey_aov_2

study2$df %>% 
  group_by(condition) %>%
  summarise(
    mean = mean(police_funding, na.rm = T),
    sd = sd(police_funding, na.rm = T)
    ) %>%
  kable(caption = "descriptive stats study 2") %>%
  kable_styling()

```

```{r}
# controlling for elevation, ignore for now
#aov_1 <- aov(police_funding ~ condition + elevation, data = study1$df)
#summary(aov_1)



#aov_2 <- aov(police_funding ~ condition + elevation, data = study2$df %>% filter(condition != "BtB"))
#summary(aov_2)
#tukey_aov_2 <- TukeyHSD(aov_2)
#tukey_aov_2

# mediation analysis


#fit.mediator = lm(elevation ~ condition, data = study2$df %>% filter(condition != "BtB"))
#fit.dv = lm(police_funding ~ condition + elevation, data = study2$df %>% filter(condition != "BtB"))
#results = mediation::mediate(fit.mediator, fit.dv, treat = 'condition', mediator = 'elevation', boot = T)
#summary(results)

```

### number of participants

##### Pilot study

```{r}

count(pilot$df)

```

##### Study 1

```{r}

count(study1$df)

```

##### Study 2

```{r}

count(study2$df)

```

### Scale reliabilities

#### Study 1

##### Police idealism

```{r}

study1$scores$idealism$alpha[3]

```

##### Elevation overall

```{r}

study1$scores$emotion$alpha[2]

```

##### Elevation - emotion terms

```{r}

study1$scores$emotion$alpha[5]

```

##### Elevation - somatic symptoms

```{r}

study1$scores$emotion$alpha[3]

```

##### Elevation - behavioral tendencies

```{r}

study1$scores$emotion$alpha[4]

```

##### Conservatism

```{r}

study1$scores$conservatism$alpha[4]

```

#### Study 2

##### Police idealism

```{r}

study2$scores$idealism$alpha[2]

```

##### BLM idealism

```{r}

study2$scores$idealism$alpha[3]

```

##### Elevation overall

```{r}

study2$scores$emotion$alpha[2]

```

##### Elevation - emotion terms

```{r}

study2$scores$emotion$alpha[5]

```

##### Elevation - somatic symptoms

```{r}

study2$scores$emotion$alpha[3]

```

##### Elevation - behavioral tendencies

```{r}

study2$scores$emotion$alpha[4]

```

##### Conservatism

```{r}

study2$scores$conservatism$alpha[4]

```

### Demographics and summary statistics

#### Study 2

```{r}


# gender
group_by(study2$df %>% filter(!is.na(gender_two_factor)), gender_two_factor) %>%
  summarise(proportion = n() / nrow(.)) %>%
  kable(caption = "gender study 2") %>%
  kable_styling()

# ethnicity

study2$df <- study2$df %>%
  mutate(
    # create binary ethnicity factor
    ethnicity_ternary = dplyr::recode_factor(
      ethnicity_factor,
      "7" = "White",
      "3" = "Black",
      "13" = "Black",
      "23" = "Black",
      "30" = "Black",
      "34" = "Black",
      "37" = "Black",
      "137" = "Black",
      "347" = "Black",
      "378" = "Black",
      "1234567" = "Black",
      .default = "other non-White",
      .missing = NULL
    )
  )

group_by(study2$df %>% filter(!is.na(ethnicity_ternary)), ethnicity_ternary) %>%
  summarise(proportion = n() / nrow(.)) %>%
  kable(caption = "ethnicity study 2") %>%
  kable_styling()

# age
summarise(
  study2$df %>% filter(!is.na(age)),
  mean(age, na.rm = TRUE),
  sd(age, na.rm = TRUE)
) %>%
  kable(caption = "age study 2") %>%
  kable_styling()

# political party
group_by(study2$df %>% filter(!is.na(major_parties)), major_parties) %>%
  summarise(proportion = n() / nrow(.)) %>%
  kable(caption = "political party study 2") %>%
  kable_styling()

# conservatism

summarise(
  study2$df %>% filter(!is.na(conservativism_overall)),
  mean(conservativism_overall, na.rm = TRUE),
  sd(conservativism_overall, na.rm = TRUE),
) %>%
  kable(caption = "conservatism study 2") %>%
  kable_styling()

# idealisms

summarise(
  study2$df %>% filter(!is.na(idealism_blm)),
  mean(idealism_blm, na.rm = TRUE),
  sd(idealism_blm, na.rm = TRUE)
) %>%
  kable(caption = "idealism_blm study 2") %>%
  kable_styling()

summarise(
  study2$df %>% filter(!is.na(idealism_police)),
  mean(idealism_police, na.rm = TRUE),
  sd(idealism_police, na.rm = TRUE)
) %>%
  kable(caption = "idealism_police study 2") %>%
  kable_styling()

summarise(
  study2$df %>% filter(!is.na(idealism_community)),
  mean(idealism_community, na.rm = TRUE),
  sd(idealism_community, na.rm = TRUE)
) %>%
  kable(caption = "idealism_community study 2") %>%
  kable_styling()

summarise(
  study2$df %>% filter(!is.na(idealism_btb)),
  mean(idealism_btb, na.rm = TRUE),
  sd(idealism_btb, na.rm = TRUE)
) %>%
  kable(caption = "idealism_btb study 2") %>%
  kable_styling()



```
### SOM: pearson and spearman correlations

#### Study 1

##### control condition

###### pearson correlations

```{r}
correlation_frame <- study1$df %>% filter(condition == "control") %>%
  dplyr::select(conservativism_overall, idealism_police, police_funding, elevation)
  
Hmisc::rcorr(as.matrix(correlation_frame), type = "pearson")

```

###### spearman correlations

```{r}
  
Hmisc::rcorr(as.matrix(correlation_frame), type = "spearman")

```

##### BLM condition

###### pearson correlations

```{r}
correlation_frame <- study1$df %>% filter(condition == "BLM") %>%
  dplyr::select(conservativism_overall, idealism_police, police_funding, elevation)
  
Hmisc::rcorr(as.matrix(correlation_frame), type = "pearson")

```

###### spearman correlations

```{r}
  
Hmisc::rcorr(as.matrix(correlation_frame), type = "spearman")

```


#### Study 2

##### control condition

###### pearson correlations

```{r}
correlation_frame <- study2$df %>% filter(condition == "control") %>%
  dplyr::select(conservativism_overall, idealism_police, police_funding, elevation, idealism_blm)
  
Hmisc::rcorr(as.matrix(correlation_frame), type = "pearson")

```

###### spearman correlations

```{r}
Hmisc::rcorr(as.matrix(correlation_frame), type = "spearman")
```

##### BLM condition

###### pearson correlations

```{r}
correlation_frame <- study2$df %>% filter(condition == "BLM") %>%
  dplyr::select(conservativism_overall, idealism_police, police_funding, elevation, idealism_blm)
  
Hmisc::rcorr(as.matrix(correlation_frame), type = "pearson")

```

###### spearman correlations

```{r}
  
Hmisc::rcorr(as.matrix(correlation_frame), type = "spearman")

```

##### BtB condition

###### pearson correlations

```{r}
correlation_frame <- study2$df %>% filter(condition == "BtB") %>%
  dplyr::select(conservativism_overall, idealism_police, police_funding, elevation, idealism_blm)
  
Hmisc::rcorr(as.matrix(correlation_frame), type = "pearson")

```

###### spearman correlations

```{r}
  
Hmisc::rcorr(as.matrix(correlation_frame), type = "spearman")

```